TreehopperFitness: Run this file for all stats, tables, and figures

### 2023-12-27 manuscript/Manuscript_runfile.Rmd
Added fig 2 and 4 to `Manuscript_runfile.Rmd`

```{r}
## Load data
surv_reg_data <- read_rds(here("saved_rds/surv_reg_data.rds"))
```

@@

# nymph survivorship
des_Nsurv.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
                           tenure="des", treatment="ant_treatment")

# egg survivorship
des_Esurv.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
                           tenure="des", treatment="ant_treatment")

@@

## Figure 5

```{r}
(desL.ant_treatment.quad.p <- egg::ggarrange(
  des_hatch.desL.ant_treatment.quad$p +
    ylab("Hatching success") +
    theme(legend.position="none"),
  des_Nsurv.desL.ant_treatment.quad$p +
    ylab("Nymph survivorship") +
    theme(legend.position="none"),
  des_Esurv.desL.ant_treatment.quad$p +
    theme(legend.position = c(0.8,0.95)) + 
    ylab("Egg survivorship") +
    ylim(0,1),
  labels=c("A","B","C"),
  ncol=3))

ggsave(here("manuscript/",
            "Figure5.png"),
       desL.ant_treatment.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

@@

@@

>>>>

```{r}
## Load data
surv_reg_data <- read_rds(here("saved_rds/surv_reg_data.rds")) %>%
    mutate(ant_treatment = ifelse(ant_treatment == "Removed", 
                                  "Ant exclusion", ant_treatment))
```

@@

# nymph survivorship
des_Nsurv.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(., survNom="n_survived", survDen="n_hatched", 
                           tenure="des", treatment="ant_treatment")

# egg survivorship
des_Esurv.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(., survNom="n_survived", survDen="med_t5eggs", 
                           tenure="des", treatment="ant_treatment")

@@

## Figure 2

```{r, fig.height = 2, fig.width = 6}
(desL.ant_treatment.quad.p <- egg::ggarrange(
  des_hatch.desL.ant_treatment.quad$p +
    xlab("Desertion date relative to hatch") +
    ylab("Hatching success") +
    theme(legend.position="none"),
  des_Nsurv.desL.ant_treatment.quad$p +
    xlab("Desertion date relative to hatch") +
    ylab("Nymph survivorship") +
    theme(legend.position="none"),
  des_Esurv.desL.ant_treatment.quad$p +
    theme(legend.position = c(0.8,0.95)) + 
    xlab("Desertion date relative to hatch") +
    ylab("Egg survivorship") +
    ylim(0,1),
  labels=c("A","B","C"),
  ncol=3))
```

@@

```{r, fig.width=3, fig.height=3}
visit_colors <- rev(unique(ggplot_build(Fig1_v1D)$data[[1]]$fill))

(guarding_durations_plot_2023 <- strats_data %>%
  filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
         clutch_initiated_order == 1, visit_ends < last_day_fID) %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  mutate(`visited in 4 days` = 
           ifelse(`visited in 4 days` == "Visited", 
                  "Visited\nwithin first 4 days", 
                  "Not visited\nwithin first 4 days")) %>%
  ggplot(aes(x=guard_duration, fill=ants)) +
  geom_histogram(binwidth = 4) +
  theme_publilia() +
  xlab("Guarding duration") +
  ylab("Number of females") +
  scale_y_continuous(breaks = c(0,4,8),
                     labels = label_number(accuracy = 1)) +
  scale_color_manual(values = c("black", "brown1")) +
  scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = 20, linetype="dashed", 
                color = "gray", size=1) +
  ggh4x::facet_grid2(vars(`visited in 4 days`, ants), 
                     strip = hist_strips) +
  theme(strip.background = element_rect(color = NA),
        strip.text = element_text(size = 12),
        legend.justification = c(1,1),
        legend.position = c(1,0.2),
        legend.text = element_text(size = 12)) +
  geom_text(data = hatch_text,
            aes(x = 20, y = Inf, label = label),
            hjust = -0.1, vjust = 0, color = "gray", fontface = "bold") +
  coord_cartesian(clip = "off"))
```

@@

```{r, fig.width=3, fig.height=2}

# non-parametric: Kruskall-Wallis test followed by Dunn test or pairwise wilcox tests
vis_cat_v1.data <- strats_data %>%
  left_join(first_visit_cuts) %>%
  mutate(vis_cat = ifelse(num_at_init > 1,
                          "0",
                          ifelse(is.na(first_visit_starts),
                                 "never visited",
                                 ifelse(first_visit_cut=="(0,4]", "1 to 4", "5+"))),
         vis_cat = factor(vis_cat, levels = c("0","1 to 4",
                                              "5+","never visited"))) %>%
  filter(!females_removed, mom_at_init, 
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID,
         # ** There was one female (E_Gkgg) which was on the eggs before and after but not ON the initiation date.
         # I suspect I missed her in the field or she may have left and come back. In any case she was never visited
         # and deserted 20 days after initiation and we have plenty such data points, so I think it's safe to ignore.
         !is.na(vis_cat))

(Fig1_v1D <- ggplot(data = vis_cat_v1.data, 
       aes(y = guard_duration, x = vis_cat, group = vis_cat)) +
  #geom_boxplot(outlier.shape = NA) +
  geom_violin(aes(fill=vis_cat%in%c("0","1 to 4")), color = NA, trim=T, size=2, alpha=0.50) +
  geom_jitter(aes(color=vis_cat%in%c("0","1 to 4")), width=0.1, size=3) +
  theme_publilia() +
  scale_color_brewer(palette="Set2") + scale_fill_brewer(palette="Set2") +
  xlab("First day clutch was visited (Days since clutch initiated)") +
  ylab("Guarding duration of initiating female (days)") +
  theme(legend.position = "none"))

# Visualization: box plots with p-values
Fig1_v1D +
    geom_text(data=strats_cuts_v1.multcompLetters, 
              aes(x=vis_cat, y=-4, label=label, 
                  color=vis_cat%in%c("0","1 to 4")), 
              fontface="bold", size=6) +
  xlab("Day first visited (Days since initiation)") +
  ylab("Guard duration of initiating female") +
  theme(legend.position = "none")
```
